\newglossaryentry{blockchain}{
  name=blockchain,
    description={A blockchain is a path through an acyclic, directed graph attaching transactions through cryptographic hashes}
}

\newglossaryentry{smart contract}{
  name={smart contract},
    description={A program designed and compiled for execution on a blockchain Multiple users may interact with the contract and may be assured that the contract will behave precisely as written between all participants}
}

\newglossaryentry{mesh network}{
  name={mesh network},
    description={A series of devices connected directly to one another by a service, intending to facilitate direct and simplified transfer of information between the devices}
}

\newglossaryentry{web of trust}{
  name={web of trust},
    description={A cryptographic concept where signatures on a key may be used to inform whether that key is valid and trustworthy}
}

\newglossaryentry{miner}{
  name={miner},
    description={A computer system tasked with mathematically validating transactions on the blockchain},
    plural={miners}
}

\newglossaryentry{web3}{
  name={web3},
    description={A library of standardized functions which allow interaction with the Ethereum network from a client program}
}

\newglossaryentry{test RPC}{
  name={test RPC},
    description={A server application which resides on the local computer and creates a connection with a mock copy of an Ethereum blockchain. These are often used for testing and debugging purposes for clients and smart contracts}
}

\newglossaryentry{gas}{
  name={gas},
    description={In Ethereum, gas is a volume of Ether paid as a transaction fee which assigns an upper limit for the amount of time a transaction may take. This is particularly useful in preventing impratically long operations}
}

\newglossaryentry{transaction}{
  name={transaction},
    description={In the context of cryptocurrency, a cryptographically verifiable payload containing information, financial or otherwise, being transmitted between two parties}
}

\newglossaryentry{mainnet}{
  name={mainnet},
    description={As opposed to a test network, the actual Ethereum environment where exchanges of value and processing occur}
}

\newglossaryentry{node}{
  name={node},
    description={A computer which has downloaded and actively processes a full local copy of the entire blockchain.}
}

\newglossaryentry{light client}{
  name={light client},
    description={A minimal client that uses the much smaller cryptographical root rather than the entire contents of the blockchain.}
}

\newglossaryentry{Ethereum}{
  name={Ethereum},
    description={A decentralized computer built on a blockchain model.}
}

\newglossaryentry{Identity management}{
    name={Identity Management},
    description={The process of associating a human user with a Contact address, similar to how a person is associated with a given email address or phone number.}
}

\newglossaryentry{Ether}{
    name={Ether},
    description={Abbreviated ETH, Ether is the cryptocurrency that powers the Ethereum ecosystem. This asset can be used as a currency or store of value, or it can be used to fuel the execution of smart contracts.}
}

\newglossaryentry{private key}{
    name={private key},
    description={In asymmetric encryption, the unique, secret value which is used to decrypt messages from other senders.}
}

\newglossaryentry{public key} {
    name={public key},
    description={The cryptographic key that is used to encrypt a message so that \textit{only} the recipient's private key has the ability to decipher it.}
}

\newglossaryentry{synced}{
    name={synced},
    description={In the context of Ethereum, syncing means allowing a running node to download every recorded change in the state of the blockchain. This allows the computer to perform its own instructions with the entire history in mind.}
}

\newglossaryentry{dependency}{
    name={dependency},
    description={A set of external objects and references from another source that a program needs to run.},
    plural={dependencies}
}

\newglossaryentry{command-line}{
    name={command-line},
    description={A program that uses a text-based command-and-response model for interacting with users rather than visual directives or feedback.}
}